---
title: "Prayer Experiment Analysis"
author: "Eleanor Schille-Hudson"
date: '2022-09-13'
output:
  html_document: 
    toc: yes
    toc_depth: 4
    toc_float: yes
---


# Prelim (libraries, data, processing, re-coding)
```{r setup, include=FALSE}
#this includes code in the knitted doc 
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Packages
I'm trying out a new and more efficient way of loading in packages! 
```{r include=FALSE, warnings=FALSE}
# Package names
packages <- c("ggplot2", "dplyr", "tidyr", "knitr", "corrplot", "tidyverse", "tidytext", "purrr", "gridExtra", "ggridges", "rjags", "BEST", "ggpubr", "GGally", "stringr", "brms")

## NOTE
# I also installed (with much trial and tribulation) rstan and brms for Bayesian regressions, but NOT putting that up here. All done in the console 

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
invisible(lapply(packages, library, character.only = TRUE))
```

## Loading Data 
```{r include=FALSE, warnings=FALSE}
# Setting working directory
#setwd("~/Library/CloudStorage/OneDrive-IndianaUniversity/Files/Research Projects/Prayer/Experiment/Data")

#on new laptop!
setwd("/Users/erbsh/Documents/Prayer/Experiment/Data")

# Loading in all PRAYER condition data from Qualtrics
p_raw <- read_csv("PrayerExp_Prayer_Clean.csv")

# Loading in all TALK condition data from Qualtrics
### note: i've renamed this conidition lablel "think" for clarity of communication/ideas
t_raw <- read_csv("PrayerExp_Talk_Clean.csv")

# Loading in table of label keys
labels <- read_csv("question_label_coding.csv")
```
## Data Cleaning
```{r include=FALSE}
# combining p_raw and t_raw into df_raw
df_raw <- bind_rows(p_raw, t_raw)

# selecting the columns I want for df
df <- df_raw %>% select(ResponseId, initials, age, gender, churched, church_type, 
                        importance_rel, freq_prayer, importance_pray, previous,
                        problem_articulation, closer, ideas, plan, motivation, optimism, 
                        connected, positive, charity, relief, result, 
                        condition, condition_num)

# recoding variables as factors 
df <- df %>% mutate(gender=factor(gender),
                        churched=factor(churched, levels=c("Never", "On special occasions (like Christmas & Easter)", "A few times a year", "Once a month", "A few times a month", "Once a week", "More than once a week")),
                        freq_prayer=factor(freq_prayer, levels=c("Never", "A few times a year", "Once a month", "A few times a month", "Once a week", "Multiple times a week", "Daily", "Multiple times a day")))
```

# Analysis

## Descriptive Stats

Here's a very nifty catchall purrr command I just learned!
```{r}
#summarizing overall
df %>%
  map(summary)

#this summarizes all the columns split by condition
df %>%                              
  split(.$condition) %>%
  map(summary)
```
## Church Type

```{r}
df$church_type

df <- df %>% mutate(church_type_fix = tolower(df$church_type)) #making new column and lowercase
df$church_type_fix <- gsub("[()]", "", df$church_type_fix) #removing parentheses
df$church_type_fix <- gsub("[?]", "", df$church_type_fix) #removing question marks
df$church_type_fix <- gsub("[.]", "", df$church_type_fix) #removing periods
df$church_type_fix <- gsub("[/]", "", df$church_type_fix) #removing /


df$church_type_fix <- df$church_type_fix %>% 
  gsub(pattern="catholic most often|catholic parish", replacement="catholic") %>% 
  gsub(pattern="anglican|anglican catholic|episcopal and african methodist episcopal|i go to the episcopal church but i'm an orthodox", replacement="episcopal") %>%
  gsub(pattern="non-denominational|christian and missionary alliance", replacement="nondenominational") %>%
  gsub(pattern="liturgical baptist|non denominational  baptist|evangelical church reformed baptist denomination|mennonite|brethren",replacement="baptist") %>%
  gsub(pattern="evangelical prebyterian|christian presbyterian|presbyterian pcusa|presbyterian church|orthodox presbyterian church",replacement="presbyterian") %>%
  gsub(pattern="united methodist|wesleyan|currently online, united methodist|on-line united methodistchurch|umc",replacement="methodist") %>%
  gsub(pattern="elca|lutheran elca",replacement="lutheran") %>% 
  gsub(pattern="disciples of christ--liberal protestant|liturgical protestant|christian|mainline liturgical", replacement="unspecified protestant")

church_list_raw <- df %>% group_by(church_type_fix) %>% dplyr::summarize(n=n()) %>% ungroup() %>% arrange(-n)

#also with avg ages
church_list_raw_age <- df %>% group_by(church_type_fix) %>% dplyr::summarize(n=n(),age=mean(age)) %>% ungroup() %>% arrange(-n)

# making even smaller categories
df$church_type_gross <- df$church_type_fix %>%
  gsub(pattern="nondenominational|baptist", replacement="evangelical") %>%
  gsub(pattern="lutheran|unspecified protestant|presbyterian", replacement="mainline protestant")

church_list_gross <- df %>% group_by(church_type_gross) %>% dplyr::summarize(n=n()) %>% ungroup() %>% arrange(-n)
church_list_gross <- church_list_gross %>% filter(n>2)


###JUST FOR FUTURE REFERENCE i'm making a special lil df minus the one person who says "the world is her church"
df99 <- df %>% filter(str_detect(church_type_fix, 'sometimes i say the world is my church and that about sums it up') == FALSE)
```

## Frequency of Prayer
```{r}
# breakdown of info 
summary(df$freq_prayer)
freq_prayer_freq <- as.data.frame(table(df$freq_prayer))

# bar plot 
freq_prayer_plot <- ggplot(freq_prayer_freq, aes(x = Var1, y = Freq)) +  # Plot with values on top
  theme_light() + 
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  geom_bar(stat = "identity", fill="dodgerblue1") +
  geom_text(aes(label = Freq), vjust = 0) +
  ggtitle("How often do you spontaneously pray by yourself?")
show(freq_prayer_plot)
```

## Graphing Response Distributions 

This is a graph of the distribution of participants' responses, question by question. Distributions for each condition are mapped on top of one another, represented by different colors. 

```{r}
# just starting with age 
## histogram
ggplot(df, aes(x=age, fill=condition)) + 
  geom_histogram(position = "identity", alpha = 0.2, bins=50) + 
  ggtitle("age")

## density plot
ggplot(df, aes(x=age, fill=condition)) + 
  geom_density(alpha=0.6, kernel="rectangular") + 
  ggtitle("age")

ggplot(df, aes(x=age, fill=condition)) + 
  geom_density(alpha=0.6, kernel="triangular") + 
  ggtitle("age")

ggplot(df, aes(x=age, fill=condition)) + 
  geom_density(alpha=0.6, kernel="optcosine") + 
  ggtitle("age")

ggplot(df, aes(x=age, fill=condition)) + 
  geom_density(alpha=0.6) + 
  ggtitle("age")
```

### Histograms

```{r}
# list of measures
measures <- c("importance_rel", "importance_pray", "previous", "problem_articulation", "closer", "ideas", "plan", "motivation", "optimism", "connected", "positive", "charity", "relief", "result") 

# using lapply to plot histograms for each measure 
hist_list <- lapply(measures, function(each_measure) {
  ggplot(df, aes_string(each_measure, fill="condition")) + 
    geom_histogram(position = "identity", alpha = 0.4, bins=50) +
    ggtitle(str_c(each_measure, " split by condition"))  # Title of the plot
})

h1 <- marrangeGrob(hist_list, nrow=1, ncol=1)
h1
```

### Faceted Histograms (fix on 1/27/23)
```{r, fig.asp = 1}
#connected
conn_med <- df %>% 
  group_by(condition) %>% 
  mutate(medn = median(connected),
         m = mean(connected))

cmp <- conn_med %>% 
  ggplot(aes(connected, fill=condition)) + 
  theme_light() +
  geom_histogram(position = "identity") +
  facet_wrap(~condition, nrow=2) +
  geom_vline(aes(xintercept= m, group=condition, color=condition), linetype="dashed") +
  #annotate(label = paste("Median =", medn)) +
  labs(title = "I feel more connected to the person after ___ about the \nsituation.", 
       x = "Agreement Score from 0-100",
       y = "Frequency") +
  theme(plot.title = element_text(size = 15),
        axis.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        legend.position = "none", 
        strip.text.x = element_text(size = 15))


#problem_articulation
prob_art_med <- df %>% 
  group_by(condition) %>% 
  mutate(medn = median(problem_articulation))

pamp <- prob_art_med %>% 
  ggplot(aes(problem_articulation, fill=condition)) + 
  theme_light() +
  geom_histogram(position = "identity") +
  facet_wrap(~condition, nrow=2) +
  geom_vline(aes(xintercept= medn, group=condition, color=condition), linetype="dashed") +
  #annotate(label = paste("Median =", medn)) +
  ggtitle("I understand the situation I am facing better as a result of praying about it.") 

#relief
rel_med <- df %>% 
  group_by(condition) %>% 
  mutate(medn = median(relief), 
         m = mean(relief))

rmp <- rel_med %>% 
  ggplot(aes(relief, fill=condition)) + 
  theme_light() +
  geom_histogram(position = "identity") +
  facet_wrap(~condition, nrow=2) +
  geom_vline(aes(xintercept= m, group=condition, color=condition), linetype="dashed") +
  #annotate(label = paste("Median =", medn)) +
  labs(title = "I feel a sense of relief after ___ about the situation.", 
       x = "Agreement Score from 0-100",
       y = "Frequency") +
  theme(plot.title = element_text(size = 15),
        axis.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        legend.position = "none", 
        strip.text.x = element_text(size = 15))

#result
res_med <- df %>% 
  group_by(condition) %>% 
  mutate(medn = median(result), 
         m = mean(result))

resmp <- res_med %>% 
  ggplot(aes(result, fill=condition)) + 
  theme_light() +
  geom_histogram(position = "identity") +
  scale_y_continuous(n.breaks= 4) +
  facet_wrap(~condition, nrow=2) +
  geom_vline(aes(xintercept= m, group=condition, color=condition), linetype="dashed") +
  #annotate(label = paste("Median =", medn)) +
  labs(title = "I think something will change with this person as a result \nof ___ about the situation.", 
       x = "Agreement Score from 0-100",
       y = "Frequency") +
  theme(plot.title = element_text(size = 15),
        axis.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        legend.position = "none", 
        strip.text.x = element_text(size = 15))

#positive
pos_med <- df %>% 
  group_by(condition) %>% 
  mutate(medn = median(positive))

pmp <- pos_med %>% 
  ggplot(aes(positive, fill=condition)) + 
  theme_light() +
  geom_histogram(position = "identity") +
  facet_wrap(~condition, nrow=2) +
  geom_vline(aes(xintercept= medn, group=condition, color=condition), linetype="dashed") +
  #annotate(label = paste("Median =", medn)) +
  ggtitle("I feel more positively towards the person after praying about the situation.") 

#previous
prev_med <- df %>% 
  group_by(condition) %>% 
  mutate(medn = median(previous))

prevmp <- prev_med %>% 
  ggplot(aes(previous, fill=condition)) + 
  theme_light() +
  geom_histogram(position = "identity") +
  facet_wrap(~condition, nrow=2) +
  geom_vline(aes(xintercept= medn, group=condition, color=condition), linetype="dashed") +
  #annotate(label = paste("Median =", medn)) +
  ggtitle("I have prayed about this particular situation before.") 

#plan
plan_med <- df %>% 
  group_by(condition) %>% 
  mutate(medn = median(plan))

planmp <- plan_med %>% 
  ggplot(aes(plan, fill=condition)) + 
  theme_light() +
  geom_histogram(position = "identity") +
  facet_wrap(~condition, nrow=2) +
  geom_vline(aes(xintercept= medn, group=condition, color=condition), linetype="dashed") +
  #annotate(label = paste("Median =", medn)) +
  ggtitle("I have a clear sense of what action I should take in this conflict with this person going forward.")

#new ideas
ideas_med <- df %>% 
  group_by(condition) %>% 
  mutate(medn = median(ideas))

ideasmp <- ideas_med %>% 
  ggplot(aes(ideas, fill=condition)) + 
  theme_light() +
  geom_histogram(position = "identity") +
  facet_wrap(~condition, nrow=2) +
  geom_vline(aes(xintercept= medn, group=condition, color=condition), linetype="dashed") +
  #annotate(label = paste("Median =", medn)) +
  ggtitle("I have new ideas or a new plan for how to solve this conflict with this person going forward.")
```

### Grouped Scatterplots
```{r}
ggplot(df, aes(x=condition, y=connected, color=condition)) +
  geom_point() +
  geom_jitter() +
  geom_violin(alpha=0) +
  ggtitle("How connected do you feel to the person after praying/thinking about them?")


# using lapply to plot grouped scatterplots for each measure 
gs_list <- lapply(measures, function(each_measure) {
  ggplot(df, aes_string(x="condition", y=each_measure, color="condition")) + 
    geom_point() +
    geom_jitter() +
    geom_violin(alpha=0) +
    ggtitle(str_c(each_measure, " split by condition"))  # Title of the plot
})

gs1 <- marrangeGrob(gs_list, nrow=1, ncol=1)
gs1
```
### Cleaned Up Density Plots (fix on 1/27/23)
```{r}
#connected 
ggplot(df, aes(x=condition, y=connected, color=condition)) +
  theme_classic() +
  geom_point(alpha=0.3) +
  geom_violin(alpha=0) +
  ggtitle("I feel more connected to the person after praying/thinking about the situation.")
```

### Density Plots 

```{r}
# using lapply to plot histograms for each measure 
dens_list <- lapply(measures, function(each_measure) {
  ggplot(df, aes_string(each_measure, fill="condition")) + 
    geom_density(alpha=0.5) +
    ggtitle(str_c(each_measure, " split by condition"))  # Title of the plot
})

d1 <- marrangeGrob(dens_list, nrow=1, ncol=1)
d1
```

### Ridgeline Plots split by median age and condition 

```{r}
# adding a column that says if they are below or above median age 
med_age = if_else(df$age >= median(df$age), "age 43+", "< age 43")
df$med_age <- med_age

#making med_age a factor
df <- df %>% mutate(med_age=factor(med_age, levels=c("< age 43", "age 43+")))

#making the ridgeline plots 
ridge_list <- lapply(measures, function(each_measure) {
  ggplot(df, aes_string(each_measure, y="med_age", fill="condition")) + 
    geom_density_ridges(alpha=0.5) +
    ggtitle(str_c(each_measure, " split by median age & condition"))  # Title of the plot
})

r1 <- marrangeGrob(ridge_list, nrow=1, ncol=1)
r1
```

### Ridgeline Plots split by how often people go to church and condition 
```{r}
ridge_list_c <- lapply(measures, function(each_measure) {
  ggplot(df, aes_string(each_measure, y="churched", fill="condition")) + 
    geom_density_ridges(alpha=0.5) +
    ggtitle(str_c(each_measure, " split by churched & condition"))  # Title of the plot
})

r2 <- marrangeGrob(ridge_list_c, nrow=1, ncol=1)
r2
```

### Ridgeline Plots split by how often people pray and condition 
```{r}
ridge_list_p <- lapply(measures, function(each_measure) {
  ggplot(df, aes_string(each_measure, y="freq_prayer", fill="condition")) + 
    geom_density_ridges(alpha=0.5) +
    ggtitle(str_c(each_measure, " split by freq_prayer & condition"))  # Title of the plot
})

r3 <- marrangeGrob(ridge_list_p, nrow=1, ncol=1)
r3
```

### Corrplot of all numerical measures split by condition 
```{r}
# creating a df for the correlation 
#you could also think about this as a df of just the (numerical) measures of interest
df_cor <- df %>% select(-ResponseId, -initials, -gender, -churched, -church_type, -freq_prayer, -condition, -med_age, -church_type_fix, -church_type_gross)

#________-------________--------_________------____

##PRAYER

# filtering for PRAYER condition
df_cor_p <- df_cor %>% filter(condition_num==0)
df_cor_p <- df_cor_p %>% select(-condition_num)

#running the actual correlation
cor_p <- cor(df_cor_p)

#visualizing nicely :) 
corrplot::corrplot(cor_p, title="Prayer Condition",mar=c(0,0,1,0))

#________-------________-------________------____

##TALK

# fitering for TALK condition
df_cor_t <- df_cor %>% filter(condition_num==1)
df_cor_t <- df_cor_t %>% select(-condition_num)

#running the actual correlation
cor_t <- cor(df_cor_t)

#visualizing nicely :) 
corrplot::corrplot(cor_t, title="Talk Condition", mar=c(0,0,1,0))

```
### Scatterplot of measures vs. previous
I'm curious if there were "bleed through" effects in the talk condition depending on how much people had prayed about the situation in the past. 
```{r}
scatter_list <- lapply(measures, function(each_measure) {
  ggplot(df_cor_t, aes_string(x="previous", y=each_measure)) + 
    geom_point(color="cornflowerblue") +
    geom_smooth(method="lm", color="darkgrey", se=FALSE) +
    stat_regline_equation(label.y = 83, aes(label = ..eq.label..)) +
    stat_regline_equation(label.y = 75, aes(label = ..rr.label..)) +
    ggtitle(str_c(each_measure, " plotted against previous"))  # Title of the plot
})

s1 <- marrangeGrob(scatter_list, nrow=1, ncol=1)
s1
```

### Scatterplot of measures vs age
```{r}
# TALK CONDITION
scatter_list_age_talk <- lapply(measures, function(each_measure) {
  ggplot(df_cor_t, aes_string(x="age", y=each_measure)) + 
    geom_point(color="cornflowerblue") +
    geom_smooth(method="lm", color="darkgrey", se=FALSE) +
    stat_regline_equation(label.y = 83, aes(label = ..eq.label..)) +
    stat_regline_equation(label.y = 75, aes(label = ..rr.label..)) +
    ggtitle(str_c("Talk condition: age vs. " ,each_measure))  # Title of the plot
})

s2_talk <- marrangeGrob(scatter_list_age_talk, nrow=1, ncol=1)
s2_talk

# PRAYER CONDITION
scatter_list_age_pray <- lapply(measures, function(each_measure) {
  ggplot(df_cor_p, aes_string(x="age", y=each_measure)) + 
    geom_point(color="salmon") +
    geom_smooth(method="lm", color="darkgrey", se=FALSE) +
    stat_regline_equation(label.y = 83, aes(label = ..eq.label..)) +
    stat_regline_equation(label.y = 75, aes(label = ..rr.label..)) +
    ggtitle(str_c("Prayer condition: age vs. " ,each_measure))  # Title of the plot
})

s2_pray <- marrangeGrob(scatter_list_age_pray, nrow=1, ncol=1)
s2_pray
```


## Bayesian T-Tests
For these, I am using John Kruschke's BEST (Bayesian Estimation Supersedes the t-Test) (Meredith & Kruschke, 2021). I am using the BEST package, which uses JAGS. I am not informing my priors at all. In each case, mu1 is the prayer group and mu2 is the talk group. I have a separate estimation of the difference of means for each of my measures. 

### MCMC
```{r}
# "My faith/religion/spirituality is important to me."                                                
BEST_importance_rel <- BESTmcmc(df_cor_p$importance_rel, df_cor_t$importance_rel, parallel = FALSE)     
# "Prayer is an important part of my faith life."    
BEST_importance_pray <- BESTmcmc(df_cor_p$importance_pray, df_cor_t$importance_pray, parallel = FALSE)  
# "I have prayed about this particular situation before."     
BEST_previous <- BESTmcmc(df_cor_p$previous, df_cor_t$previous, parallel = FALSE)  

# "I understand the situation I am facing better as a result of praying about it."  
BEST_problem_articulation <- BESTmcmc(df_cor_p$problem_articulation, df_cor_t$problem_articulation, parallel = FALSE)  

# "I am closer to solving the conflict with this person."                                             
BEST_closer <- BESTmcmc(df_cor_p$closer, df_cor_t$closer, parallel = FALSE)  

# "I have new ideas or a new plan for how to solve this conflict with this person going forward."     
BEST_ideas <- BESTmcmc(df_cor_p$ideas, df_cor_t$ideas, parallel = FALSE)  

# "I have a clear sense of what action I should take in this conflict with this person going forward."
BEST_plan <- BESTmcmc(df_cor_p$plan, df_cor_t$plan, parallel = FALSE)  

# "I am motivated to resolve conflict with this person after praying about the situation."            
BEST_motivation <- BESTmcmc(df_cor_p$motivation, df_cor_t$motivation, parallel = FALSE)  

# "I am optimistic that there is a resolution to this conflict after praying about the situation."    
BEST_optimism <- BESTmcmc(df_cor_p$optimism, df_cor_t$optimism, parallel = FALSE)  

# "I feel more connected to the person after praying about the situation."                            
BEST_connected <- BESTmcmc(df_cor_p$connected, df_cor_t$connected, parallel = FALSE)  

# "I feel more positively towards the person after praying about the situation."                      
BEST_positive <- BESTmcmc(df_cor_p$positive, df_cor_t$positive, parallel = FALSE)  

# "I feel more charitable towards the person after praying about the situation."                      
BEST_charity <- BESTmcmc(df_cor_p$charity, df_cor_t$charity, parallel = FALSE)  

# "I feel a sense of relief after praying about the situation."                                       
BEST_relief <- BESTmcmc(df_cor_p$relief, df_cor_t$relief, parallel = FALSE)  

# "I think something will change with this person as a result of praying about the situation."        
BEST_result <- BESTmcmc(df_cor_p$result, df_cor_t$result, parallel = FALSE)  
```

### Plots & Summaries 
I don't want to run those analyses more than I have to, so I'm plotting separately
```{r}
#1 "My faith/religion/spirituality is important to me."   
plot(BEST_importance_rel)     
summary(BEST_importance_rel)

#2 "Prayer is an important part of my faith life."    
plot(BEST_importance_pray)  
summary(BEST_importance_pray)

#3 "I have prayed about this particular situation before."     
plot(BEST_previous)  
summary(BEST_previous)

#4 "I understand the situation I am facing better as a result of praying about it."  
plot(BEST_problem_articulation)  
summary(BEST_problem_articulation)

#5 "I am closer to solving the conflict with this person."                                             
plot(BEST_closer)  
summary(BEST_closer)

#6 "I have new ideas or a new plan for how to solve this conflict with this person going forward."     
plot(BEST_ideas)  
summary(BEST_ideas)

#7 "I have a clear sense of what action I should take in this conflict with this person going forward."
plot(BEST_plan)  
summary(BEST_plan)

#8 "I am motivated to resolve conflict with this person after praying about the situation."            
plot(BEST_motivation)  
summary(BEST_motivation)

#9 "I am optimistic that there is a resolution to this conflict after praying about the situation."    
plot(BEST_optimism)  
summary(BEST_optimism)

#10 "I feel more connected to the person after praying about the situation."                          
plot(BEST_connected) 
summary(BEST_connected)

#11 "I feel more positively towards the person after praying about the situation."                    
plot(BEST_positive) 
summary(BEST_positive)

#12 "I feel more charitable towards the person after praying about the situation."                    
plot(BEST_charity) 
summary(BEST_charity)

#13 "I feel a sense of relief after praying about the situation."                                     
plot(BEST_relief)  
summary(BEST_relief)

#14 "I think something will change with this person as a result of praying about the situation."      
plot(BEST_result)
summary(BEST_result)
```

## Regular Regressions lol 
```{r}
df <- df %>% mutate(condition = factor(condition))
contrasts(df$condition) <- cbind("pray" = c(1, -1))
m.connect <- glm(formula = connected ~ scale(age)*condition,
                 data = df,
                 family = gaussian
                 )

m.result <- glm(formula = result ~ scale(age)*condition,
                 data = df,
                 family = gaussian
                 )

m.relief <- glm(formula = relief ~ scale(age)*condition,
                 data = df,
                 family = gaussian
                 )
```

## Bayesian Regressions 

### MCMC
Only run this one time. It's slow. 
```{r}
#problem_articulation 
model_problem_articulation <- brm(formula = problem_articulation ~ scale(age)*condition,
                       data = df)
#closer               
model_closer <- brm(formula = closer ~ scale(age)*condition,
                       data = df)
#ideas                
model_ideas <- brm(formula = ideas ~ scale(age)*condition,
                       data = df)
#plan                 
model_plan <- brm(formula = plan ~ scale(age)*condition,
                       data = df)
#motivation 
model_motivation <- brm(formula = motivation ~ scale(age)*condition,
                       data = df)
#optimism  
model_optimism <- brm(formula = optimism ~ scale(age)*condition,
                       data = df)
#connected 
df <- df %>% mutate(condition = factor(condition))
contrasts(df$condition) <- cbind("pray" = c(1, -1))
model_connected <- brm(formula = connected ~ scale(age)*condition,
                       data = df)
            
#positive 
model_positive <- brm(formula = positive ~ scale(age)*condition,
                       data = df)
#charity  
model_charity <- brm(formula = charity ~ scale(age)*condition,
                       data = df)
#relief   
model_relief <- brm(formula = relief ~ scale(age)*condition,
                       data = df)
#result  
model_result <- brm(formula = result ~ scale(age)*condition,
                       data = df)
```

### Summaries 
```{r}
#problem_articulation 
summary(model_problem_articulation) 
#checking how many times in MCMC chain age slope was bigger than age - talk age interaction (is prayer a meaningful training effect)
ps_pa <- posterior_samples(model_problem_articulation)
ps_pa_mean <- mean(ps_pa$b_scaleage > (-1*(ps_pa$b_scaleage - ps_pa$`b_scaleage:conditionthink`))) 
ps_pa_mean

#closer               
summary(model_closer)
#checking how many times in MCMC chain age slope was bigger than age - talk age interaction (is prayer a meaningful training effect)
ps_c <- posterior_samples(model_closer)
ps_c_mean <- mean(ps_c$b_scaleage > (-1*(ps_c$b_scaleage - ps_c$`b_scaleage:conditionthink`))) 
ps_c_mean

#ideas                
summary(model_ideas)
#checking how many times in MCMC chain age slope was bigger than age - talk age interaction (is prayer a meaningful training effect)
ps_i <- posterior_samples(model_ideas)
ps_i_mean <- mean(ps_i$b_scaleage > (-1*(ps_i$b_scaleage - ps_i$`b_scaleage:conditionthink`))) 
ps_i_mean

#plan                 
summary(model_plan)
#checking how many times in MCMC chain age slope was bigger than age - talk age interaction (is prayer a meaningful training effect)
ps_p <- posterior_samples(model_plan)
ps_p_mean <- mean(ps_p$b_scaleage > (-1*(ps_p$b_scaleage - ps_p$`b_scaleage:conditionthink`))) 
ps_p_mean

#motivation 
summary(model_motivation)
#checking how many times in MCMC chain age slope was bigger than age - talk age interaction (is prayer a meaningful training effect)
ps_m <- posterior_samples(model_motivation)
ps_m_mean <- mean(ps_m$b_scaleage > (-1*(ps_m$b_scaleage - ps_m$`b_scaleage:conditionthink`))) 
ps_m_mean

#optimism  
summary(model_optimism)
#checking how many times in MCMC chain age slope was bigger than age - talk age interaction (is prayer a meaningful training effect)
ps_o <- posterior_samples(model_optimism)
ps_o_mean <- mean(ps_o$b_scaleage > (-1*(ps_o$b_scaleage - ps_o$`b_scaleage:conditionthink`))) 
ps_o_mean

#connected 
summary(model_connected)
#checking how many times in MCMC chain age slope was bigger than age - talk age interaction (is prayer a meaningful training effect)
ps_con <- posterior_samples(model_connected)
ps_con_mean <- mean(ps_con$b_scaleage > (-1*(ps_con$b_scaleage - ps_con$`b_scaleage:conditionthink`))) 
ps_con_mean
            
#positive 
summary(model_positive)
#checking how many times in MCMC chain age slope was bigger than age - talk age interaction (is prayer a meaningful training effect)
ps_pos <- posterior_samples(model_positive)
ps_pos_mean <- mean(ps_pos$b_scaleage > (-1*(ps_pos$b_scaleage - ps_pos$`b_scaleage:conditionthink`))) 
ps_pos_mean

#charity  
summary(model_charity)
#checking how many times in MCMC chain age slope was bigger than age - talk age interaction (is prayer a meaningful training effect)
ps_ch <- posterior_samples(model_charity)
ps_ch_mean <- mean(ps_ch$b_scaleage > (-1*(ps_ch$b_scaleage - ps_ch$`b_scaleage:conditionthink`))) 
ps_ch_mean

#relief   
summary(model_relief)
#checking how many times in MCMC chain age slope was bigger than age - talk age interaction (is prayer a meaningful training effect)
ps_r <- posterior_samples(model_relief)
ps_r_mean <- mean(ps_r$b_scaleage > (-1*(ps_r$b_scaleage - ps_r$`b_scaleage:conditionthink`))) 
ps_r_mean

#result  
summary(model_result)
#checking how many times in MCMC chain age slope was bigger than age - talk age interaction (is prayer a meaningful training effect)
ps_res <- posterior_samples(model_result)
ps_res_mean <- mean(ps_res$b_scaleage > (-1*(ps_res$b_scaleage - ps_res$`b_scaleage:conditionthink`))) 
ps_res_mean
```

### Nice Scatterplots of Age vs. Measures with Bayesian model fits 
```{r}
#problem_articulation 
problem_articulation_age <- ggplot(df, aes(x=scale(age), y=problem_articulation, color=condition)) +
    geom_point() +
    geom_abline(intercept=mean(ps_pa$b_Intercept), slope=mean(ps_pa$b_scaleage), color="#F8766D", size=1)+ 
  geom_abline(intercept=(mean(ps_pa$b_Intercept) + mean(ps_pa$b_conditionthink)), slope=(mean(ps_pa$b_scaleage) + mean(ps_pa$`b_scaleage:conditionthink`)), color="#00BFC4", size=1) +
  geom_vline(xintercept = 0, color="grey", linetype="dashed") +
  ggtitle("Problem Articulation vs. Participant Age with Bayesian Regression Model Fits")

problem_articulation_age

#closer  
closer_age <- ggplot(df, aes(x=scale(age), y=closer, color=condition)) +
    geom_point() +
    geom_abline(intercept=mean(ps_c$b_Intercept), slope=mean(ps_c$b_scaleage), color="#F8766D", size=1) +
  geom_abline(intercept=(mean(ps_c$b_Intercept) + mean(ps_c$b_conditionthink)), slope=(mean(ps_c$b_scaleage) + mean(ps_c$`b_scaleage:conditionthink`)), color="#00BFC4", size=1) +
  geom_vline(xintercept = 0, color="grey", linetype="dashed")+
  ggtitle("Closer vs. Participant Age with Bayesian Regression Model Fits")

closer_age

#ideas
ideas_age <- ggplot(df, aes(x=scale(age), y=ideas, color=condition)) +
    geom_point() +
    geom_abline(intercept=mean(ps_i$b_Intercept), slope=mean(ps_i$b_scaleage), color="#F8766D", size=1) +
  geom_abline(intercept=(mean(ps_i$b_Intercept) + mean(ps_i$b_conditionthink)), slope=(mean(ps_i$b_scaleage) + mean(ps_i$`b_scaleage:conditionthink`)), color="#00BFC4", size=1) +
  geom_vline(xintercept = 0, color="grey", linetype="dashed")+
  ggtitle("Ideas vs. Participant Age with Bayesian Regression Model Fits")

ideas_age

#plan  
plan_age <- ggplot(df, aes(x=scale(age), y=plan, color=condition)) +
    geom_point() +
    geom_abline(intercept=mean(ps_p$b_Intercept), slope=mean(ps_p$b_scaleage), color="#F8766D", size=1) +
  geom_abline(intercept=(mean(ps_p$b_Intercept) + mean(ps_p$b_conditionthink)), slope=(mean(ps_p$b_scaleage) + mean(ps_p$`b_scaleage:conditionthink`)), color="#00BFC4", size=1) +
  geom_vline(xintercept = 0, color="grey", linetype="dashed")+
  ggtitle("Plan vs. Participant Age with Bayesian Regression Model Fits")

plan_age 

#motivation  
motivation_age <- ggplot(df, aes(x=scale(age), y=motivation, color=condition)) +
    geom_point() +
    geom_abline(intercept=mean(ps_m$b_Intercept), slope=mean(ps_m$b_scaleage), color="#F8766D", size=1) +
  geom_abline(intercept=(mean(ps_m$b_Intercept) + mean(ps_m$b_conditionthink)), slope=(mean(ps_m$b_scaleage) + mean(ps_m$`b_scaleage:conditionthink`)), color="#00BFC4", size=1) +
  geom_vline(xintercept = 0, color="grey", linetype="dashed")+
  ggtitle("Motivation vs. Participant Age with Bayesian Regression Model Fits")

motivation_age

#optimism
optimism_age <- ggplot(df, aes(x=scale(age), y=optimism, color=condition)) +
    geom_point() +
    geom_abline(intercept=mean(ps_o$b_Intercept), slope=mean(ps_o$b_scaleage), color="#F8766D", size=1) +
  geom_abline(intercept=(mean(ps_o$b_Intercept) + mean(ps_o$b_conditionthink)), slope=(mean(ps_o$b_scaleage) + mean(ps_o$`b_scaleage:conditionthink`)), color="#00BFC4", size=1) +
  geom_vline(xintercept = 0, color="grey", linetype="dashed")+
  ggtitle("Optimism vs. Participant Age with Bayesian Regression Model Fits")

optimism_age

#connected 
connected_age <- ggplot(df, aes(x=scale(age), y=connected, color=condition)) +
    geom_point() +
    geom_abline(intercept=mean(ps_con$b_Intercept), slope=mean(ps_con$b_scaleage), color="#F8766D", size=1) +
  geom_abline(intercept=(mean(ps_con$b_Intercept) + mean(ps_con$b_conditionthink)), slope=(mean(ps_con$b_scaleage) + mean(ps_con$`b_scaleage:conditionthink`)), color="#00BFC4", size=1) +
  geom_vline(xintercept = 0, color="grey", linetype="dashed") +
  ggtitle("Connection vs. Participant Age with Bayesian Regression Model Fits")

connected_age

#positive  
positive_age <- ggplot(df, aes(x=scale(age), y=positive, color=condition)) +
    geom_point() +
    geom_abline(intercept=mean(ps_pos$b_Intercept), slope=mean(ps_pos$b_scaleage), color="#F8766D", size=1) +
  geom_abline(intercept=(mean(ps_pos$b_Intercept) + mean(ps_pos$b_conditionthink)), slope=(mean(ps_pos$b_scaleage) + mean(ps_pos$`b_scaleage:conditionthink`)), color="#00BFC4", size=1) +
  geom_vline(xintercept = 0, color="grey", linetype="dashed")+
  ggtitle("Positive vs. Participant Age with Bayesian Regression Model Fits")

positive_age

#charity 
charity_age <- ggplot(df, aes(x=scale(age), y=charity, color=condition)) +
    geom_point() +
    geom_abline(intercept=mean(ps_ch$b_Intercept), slope=mean(ps_ch$b_scaleage), color="#F8766D", size=1) +
  geom_abline(intercept=(mean(ps_ch$b_Intercept) + mean(ps_ch$b_conditionthink)), slope=(mean(ps_ch$b_scaleage) + mean(ps_ch$`b_scaleage:conditionthink`)), color="#00BFC4", size=1) +
  geom_vline(xintercept = 0, color="grey", linetype="dashed")+
  ggtitle("Charity vs. Participant Age with Bayesian Regression Model Fits")

charity_age

#relief  
relief_age <- ggplot(df, aes(x=scale(age), y=relief, color=condition)) +
    geom_point() +
    geom_abline(intercept=mean(ps_r$b_Intercept), slope=mean(ps_r$b_scaleage), color="#F8766D", size=1) +
  geom_abline(intercept=(mean(ps_r$b_Intercept) + mean(ps_r$b_conditionthink)), slope=(mean(ps_r$b_scaleage) + mean(ps_r$`b_scaleage:conditionthink`)), color="#00BFC4", size=1) +
  geom_vline(xintercept = 0, color="grey", linetype="dashed")+
  ggtitle("Relief vs. Participant Age with Bayesian Regression Model Fits")

relief_age

#result
result_age <- ggplot(df, aes(x=scale(age), y=result, color=condition)) +
    geom_point() +
    geom_abline(intercept=mean(ps_res$b_Intercept), slope=mean(ps_res$b_scaleage), color="#F8766D", size=1) +
  geom_abline(intercept=(mean(ps_res$b_Intercept) + mean(ps_res$b_conditionthink)), slope=(mean(ps_res$b_scaleage) + mean(ps_res$`b_scaleage:conditionthink`)), color="#00BFC4", size=1) +
  geom_vline(xintercept = 0, color="grey", linetype="dashed")+
  ggtitle("Result vs. Participant Age with Bayesian Regression Model Fits")

result_age  
  
```